\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-04 intro.tex
added comment

Classic techniques that product groups employ to test, verify and validate their systems (such as code reviews, unit testing, stress testing and fault injection) are unable to capture and control all the aforementioned sources of nondeterminism \SCComment{my comment is similar to the one in the intro: do we claim that we capture all sources of nondet?} \PDComment{only the ones that the user has mocked using the \psharp APIs, some are handled automatically like async/await, we should probably rephrase}, which causes the most tricky bugs being missed during testing and only getting exposed after a system has been put in production. Discovering and fixing bugs in production, though, is bad for business as it can cost a lot of money~\cite{tassey2002economic} and many dissatisfied customers~\cite{amazon2012aws, google2014outage}.

>>>>

Classic techniques that product groups employ to test, verify and validate their systems (such as code reviews, unit testing, stress testing and fault injection) are unable to capture and control all the aforementioned sources of nondeterminism \SCComment{my comment is similar to the one in the intro: do we claim that we capture all sources of nondet?} \PDComment{only the ones that the user has mocked using the \psharp APIs, some are handled automatically like async/await, we should probably rephrase}, which causes the most tricky bugs being missed during testing and only getting exposed after a system has been put in production. Discovering and fixing bugs in production, though, is bad for business as it can cost a lot of money~\cite{tassey2002economic} \PDComment{this citation is the famous multi-billion cost for the US economy, not sure if it should go here as we are focusing in distr systems} and many dissatisfied customers~\cite{amazon2012aws, google2014outage}.
